Scaling of Electrode-Electrolyte Interface Model Parameters In Phosphate Buffered Saline

### 2014-02-11 paper.tex
Regraph charge injection and recalculate current density

This displacement mechanism is capable of transferring charge between electrical and biological systems without damaging electrodes or tissue. \cite{Horch2004}
This behaviour is modelled by way of a Constant Phase Element (CPE); also known as a fractional capacitor.
}
{
    \color{blue}
For simulation purposes this element is realised as an array of R-C branches.~\cite{ScottSingle2013,Morrison59,Elwakil10} where the value of each R-C pair is chosen to set the slope of impedance relative to frequency. The placement of R-C pairs within the CPE is determined by Morrison's parameters $m$ and $k$, where $k$ determines the spacing, or density, of R-C branches and $m$ determines the resulting slope.
}
We measure displacement currents by sweeping the frequency of a sinusoidal stimulus across electrodes 2 and 7 of the Octrode while measuring the voltage between electrodes 2 and 3 (numbering shown in Fig.~\ref{fig:octrode}). 
This allows for the measurement of a single interface impedance in series with the resistance presented by the bulk solution. 
\begin{figure}
    \begin{center}
        \includegraphics{graphics/chargeInjectionVsFrequency.pdf}
    \end{center}
    \caption{\color{blue} Charge injected during CPE measurement for each of the six concentrations of PBS. Calculated using an effective surface area of 14\thinspace mm$^{2}$}
    \label{fig:chargeInjectionVsFrequency}
\end{figure}
{
    \color{blue}
Current density during measurements peaked at $11.5\thinspace A/m^{2}$ at 10\thinspace kHz in 1.0X PBS and fell as low as $0.0141\thinspace A/m^{2}$ at 50\thinspace mHz in 0.025X PBS. The charge injected is shown in figure~\ref{fig:chargeInjectionVsFrequency}. 
The stimulus waveform was set at 300\thinspace mV (peak) at each measurement point. The measurement instruments used are the same as those used to measure the inter-electrode resistance.
}
{
    \color{blue}
Figure~\ref{fig:CPE_Magnitude} shows the magnitude of the measured response of each of the six PBS concentrations accompanied by simulation results. Figure~\ref{fig:CPE_Phase} shows the phase response for the same measurements, again with the simulated response at each concentration. The simulated responses are generated using the optimised parameter values presented in Table~\ref{tab:CPEparams}. Those values were chosen as they give the closest match to the measured data.
}
As shown in the interface model schematic (figure~\ref{fig:schematic}), the interface contains its own internal series resistance ($R_{S}$). The resistance seen in series with the CPE will therefore be the sum of both the resistance due to the bulk resistivity of the fluid and $R_{S}$, to which we will refer as $R_{S+bulk}$.
In figure~\ref{fig:CPE_Magnitude}, the slope and magnitude of the CPE are visible below 1\thinspace Hz whereas $R_{S+bulk}$  dominates above 1\thinspace kHz; it is clear that the two do not scale similarly.
As the impedance of the CPE and $R_{S+bulk}$ are separable with frequency, these measurements can be used to determine the CPE parameters and $R_{S}$.

>>>>

This displacement mechanism is capable of transferring charge between electrical and biological systems without damaging electrodes or tissue. \cite{Horch2004}
This behaviour is modelled by way of a Constant Phase Element (CPE); also known as a fractional capacitor.
}
{
    \color{blue}
For simulation purposes this element is realised as an array of R-C branches.~\cite{ScottSingle2013,Morrison59,Elwakil10} where the value of each R-C pair is chosen to set the slope of impedance relative to frequency. The placement of R-C pairs within the CPE is determined by Morrison's parameters $m$ and $k$, where $k$ determines the spacing, or density, of R-C branches and $m$ determines the resulting slope.
}
We measure displacement currents by sweeping the frequency of a sinusoidal stimulus across electrodes 2 and 7 of the Octrode while measuring the voltage between electrodes 2 and 3 (numbering shown in Fig.~\ref{fig:octrode}). 
This allows for the measurement of a single interface impedance in series with the resistance presented by the bulk solution. 
\begin{figure}
    \begin{center}
        \includegraphics{graphics/chargeInjectionVsFrequency_magnitude}
    \end{center}
    \caption{\color{blue} Charge injected per phase during CPE measurement for each of the six concentrations of PBS. Calculated using a geometric surface area of 10\thinspace mm$^{2}$}
    \label{fig:chargeInjectionVsFrequency}
\end{figure}
{
    \color{blue}
    The geometric current density during measurements peaked at 22.59\thinspace mA/cm$^{2}$ at 5300\thinspace kHz in 1.0X PBS and fell as low as 27.66\thinspace $\mu$A/cm$^{2}$ at 50\thinspace mHz in 0.025X PBS. Charge injection per phase is shown in figure~\ref{fig:chargeInjectionVsFrequency} for each solution. 
The stimulus waveform was set at 300\thinspace mV (peak) at each measurement point. The measurement instruments used are the same as those used to measure the inter-electrode resistance.
}
{
    \color{blue}
Figure~\ref{fig:CPE_Magnitude} shows the magnitude of the measured response of each of the six PBS concentrations accompanied by simulation results. Figure~\ref{fig:CPE_Phase} shows the phase response for the same measurements, again with the simulated response at each concentration. The simulated responses are generated using the optimised parameter values presented in Table~\ref{tab:CPEparams}. Those values were chosen as they give the closest match to the measured data.
}
As shown in the interface model schematic (figure~\ref{fig:schematic}), the interface contains its own internal series resistance ($R_{S}$). The resistance seen in series with the CPE will therefore be the sum of both the resistance due to the bulk resistivity of the fluid and $R_{S}$, to which we will refer as $R_{S+bulk}$.
In figure~\ref{fig:CPE_Magnitude}, the slope and magnitude of the CPE are visible below 1\thinspace Hz whereas $R_{S+bulk}$  dominates above 1\thinspace kHz; it is clear that the two do not scale similarly.
As the impedance of the CPE and $R_{S+bulk}$ are separable with frequency, these measurements can be used to determine the CPE parameters and $R_{S}$.
